---
title: "Ass5"
author: "Daoyang E"
date: "11/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(statnet)
library(dplyr)
library(sna)
library(keyplayer)
library(NbClust)
```


### 2.1

```{r}
data <- read.csv("Manager_friends.csv", header = T)
friends <- as.matrix(data)

data2 <- read.csv("Manager_advice.csv", header = T)
advice <- as.matrix(data2)

manager<- friends+advice

#for (i in 1:21){
#  for (j in 1:21){
#    if(dat[i,j]==2)
#      dat[i,j] = 1
#  }
#}

### Convert to a manager network 
#manager <- t(dat) %*% dat
# Remove loops
diag(manager)=0

### Make a network
net <- network(manager, matrix.type="adjacency", directed=T, ignore.eval=FALSE, names.eval="value")
```


### 2.2

```{r}
degree <- degree(net, ignore.eval=FALSE) #For binary networks, set ignore.eval=TRUE.
closeness <- closeness(net, ignore.eval=FALSE, cmode="suminvundir")
betweenness <- betweenness(net, ignore.eval=FALSE, cmode="undirected")
ecent <- evcent(net, ignore.eval=FALSE)

cbind(degree, closeness, betweenness, ecent)
```

### 2.3

```{r}
### Import the attributes for nodes
att <- read.csv("Manager_att.csv", header = T, row.names = 1 )
set.vertex.attribute(net, "age", att$age )
set.vertex.attribute(net, "tenure", att$tenure )
set.vertex.attribute(net, "level", att$level )
set.vertex.attribute(net, "dept", att$dept )

### Plot the network
plot(net, displaylabels = T, edge.lwd=net%e%'value', vertex.col=att$dept)
```

### 2.4

```{r results='hide'}
model <- ergm(net~sum+nodecov("age")+nodecov("tenure")+nodefactor("level")+ nodefactor("dept")+nodematch("age")+nodematch("tenure")+nodematch("level")+nodematch("dept") +mutual +  transitiveweights, response="value", reference=~Poisson)
```

```{r}
summary(model)
```


The average connection for a vice president is $e^{-0.151169}$ times the average connection for a CEO. The average connection for a manager is $e^{-0.57618}$ times the average connection for a CEO. The average connection for a person in department 2 is $e^{-0.0825}$  times the average connection for a person in department 1. The avergae connection between a person in department 3 and department 1 is $e^{0.1716}$  times the average connection for a person in department 1The average connection between manager with the same level is $e^{0.58227}$ times the average connection between manager with different level. The average connection between manager with the same department is $e^{0.189343}$ times the average connection between manager with different department. The mutuality between two managers is $e^{ 0.874967}$ times the average connection for asymmetrical ties between managers. The average connection between manager with the same age is $e^{0.50705}$ times the average connection between manager with different department.

### 3.1

```{r}
deg <- degree(advice, cmode = "indegree")
names(deg) <- seq(1,21,1)

ids <- as.numeric(names(sort(deg, decreasing=T)[1:4]))
ids

kpcent(advice,ids,type="degree", cmode="indegree", method = "max")
```

the number of the managers with the highest individual indegree are number 2, 7, 18, 21. The unique incoming connections they have is 17.

### 3.2

```{r}
kpset(advice,size=4,type="degree", cmode="indegree", method = "max")
```

the four managers with highest group indegree is 2, 7, 18, 21. And the total number of unique incoming connections they have is 17.

### 3.3

```{r}
library(igraph)
```


```{r}
Fnet <- graph.adjacency(advice)

g <- edge.betweenness.community(Fnet)

plot(as.dendrogram(g))
```

```{r}
g$membership
```

```{r}
V(Fnet)$color=g$membership

plot(Fnet)
```

### 3.4

```{r}
set.seed(385)
nc <- NbClust(advice, min.nc=2, max.nc=8, index = "kl", method="kmeans")
nc
```

we see that, from this method, group 1, 2, 3 have rather good kmeans value.

While the edge-removal methods only left us with one group, group 1, this difference might stem from the fact that edge-removal method is better for undirected network while manager advising network is a directed network.
